Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-05 paper/paper.Rmd
attach packages in chunk buffer to make pdf compilation work

```{r buffer, fig.cap="Visualization of the 'Spatial buffering' method from package `blockCV`.", out.width="40%", fig.pos="ht"}
task = tsk("ecuador")
resampling_buffer = rsmp("spcv_buffer", theRange = 1000)
resampling_buffer$instantiate(task)

>>>>

```{r buffer, fig.cap="Visualization of the 'Spatial buffering' method from package `blockCV`.", out.width="40%", fig.pos="ht"}
library("mlr3")
library("mlr3spatiotempcv")
task = tsk("ecuador")
resampling_buffer = rsmp("spcv_buffer", theRange = 1000)
resampling_buffer$instantiate(task)
